Language learning in context via recursive pragmatic reasoning

### 2013-05-31 praglearn.tex
remove a line from 3.2, putting us back under the page limit

The model of \cite{bergen2012} differs from ours in that they then
apply further layers of pragmatic recursion on top of these marginal
distributions, which as described above removes the possibility of
learning; in their model it is only hypothetical agents who are
ignorant, while the actual speaker and listener know everything there
is to know about each other's behavior. However, the core result
carries over to our model. For example, with a uniform prior over
lexicons and $P_\text{prior}(\text{\textsc{common}}) = 0.8$,
$\text{cost}(\text{``cheap''}) = 0.5$,
$\text{cost}(\text{``expensive''}) = 1.0$, the symmetry breaks in the
appropriate way: Despite total ignorance about the conventional
system, speakers prefer to use simple words for common referents
($P_S(\text{``cheap''} | \text{\textsc{common}}) = 0.88,
P_S(\text{``cheap''} | \text{\textsc{rare}}) = 0.46$), and listeners
show a similar bias ($P_L(\text{\textsc{common}} | \text{``cheap''}) =
0.77, P_L(\text{\textsc{common}} | \text{``expensive''}) =
0.65$). This preference is somewhat weak; the critical observation is
that it exists at all, given the unbiased priors. We return to this
point in \S\ref{sec:horn-emergence}.

>>>>

The model of \cite{bergen2012} differs from ours in that they then
apply further layers of pragmatic recursion on top of these marginal
distributions, which as described above removes the possibility of
learning; in their model it is only hypothetical agents who are
ignorant, while the actual speaker and listener know everything there
is to know about each other's behavior. However, the core result
carries over to our model. E.g., with a uniform prior over
lexicons and $P_\text{prior}(\text{\textsc{common}}) = 0.8$,
$\text{cost}(\text{``cheap''}) = 0.5$,
$\text{cost}(\text{``expensive''}) = 1.0$, the symmetry breaks in the
appropriate way: Despite total ignorance about the conventional
system, speakers prefer to use simple words for common referents
($P_S(\text{``cheap''} | \text{\textsc{common}}) = 0.88,
P_S(\text{``cheap''} | \text{\textsc{rare}}) = 0.46$), and listeners
show a similar bias ($P_L(\text{\textsc{common}} | \text{``cheap''}) =
0.77, P_L(\text{\textsc{common}} | \text{``expensive''}) =
0.65$). This preference is weak; the critical point is
that it exists at all, given the unbiased priors. We return to this
\S\ref{sec:horn-emergence}.
